Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Plot label change

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x") + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + geom_smooth(method="lm") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=4)

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x") + xlab("") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=8, height=6)
@

>>>>

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x") + xlab("Scaled Score") + ylab("Scaled Lineup Score") + geom_smooth(method="lm") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=4)

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x") + xlab("") + ylab("Scaled Lineup Score") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=8, height=6)
@
